|

### 2021-06-01 01-Chp-Background.Rmd
End of day: -4243
Submission of Chapter 4 to supervisors
End of day: -3464

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
source("R/helper.R")
knitr::read_chunk("R/background.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

@@

The remaining 10-30% of cases are caused other dementia subtypes (e.g. Lewy Body dementia, frontotemporal dementia) or by progression of other neurological diseases (e.g. Parkinson's disease). [@burns2009]

@@

>>>>

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
source("R/helper.R")
knitr::read_chunk("R/01-Code-Background.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

@@

The remaining 10-30% of cases are caused other dementia subtypes (e.g. Lewy Body dementia, frontotemporal dementia) or by progression of other neurological diseases (e.g. Parkinson's disease).[@burns2009]

@@

(ref:thesisOverview-scaption) Summary of studies included in this thesis

### 2021-06-01 03-Chp-Systematic-Review.Rmd
End of day: -3799
End of day: -3464

---
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: default
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = TRUE}
"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
```

@@

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
knitr::read_chunk("R/Chp2-Systematic-Review.R")
```

@@

-   Examine how many times a primary study was included in a review\
-   Look at whether searching preprints made any difference to my results
-   Could apply ROBIS to previous reviews to see how they stack-up?

@@

Based on the review of prev, no previous

@@

Following guidance for a dose response meta-analysis, we picked m

@@

@@

@@

@@

@@

<!-- ------------------------------------------------------------------------- -->

```{r gwet-setup, results="hide", message=FALSE, echo = FALSE}
```

```{r gwet-table, message=FALSE, results="asis", echo = FALSE}
```

<!-- ------------------------------------------------------------------------- -->

<!--- Need example table here, showing relevant cells --->

@@

@@

@@

### Publication bias

@@

One particularly interesting meta-bias potentially applicable in this review is the definition

@@

@@

@@

## Conclusion

>>>>

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
```

@@

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
source("R/helper.R")
knitr::read_chunk("R/03-Code-Systematic-Review.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

@@

-   Examine how many times a primary study was included in a review\
-   Look at whether searching preprints made any difference to my results
-   Could apply ROBIS to previous reviews to see how they stack-up? (This may be done as part of Georgia's summer project)

@@

Based on the review of prev, no previous evidence synthesis exercise attempted to examine all available literature simultaneously.

Only by looking across all available evidence can

@@

Following guidance for a dose response meta-analysis, we picked midpoint for all studies where bands were provided (extremely common in the case of lipids)

This analysis was unusual, as multiple methods of intergration and analysis were required with data spannign many forms.

@@

<!-- TODO Cite release version of this tool, and just use domain based approach -->

@@

<!-- TODO This next bit is not true -->

@@

<!-- TODO Cite MR tool here from malmuk, see info from Francesca -->

@@

## Studification

In the advent of multiple papers reporting results on the same cohort, but say, at different time points, I used a process of studifiction to build out the most comprehensive accounts of the studies and results from as many published articles were applicable.

## Following up with authors

As part of the IPD analysis, relevant cohort studies were identified and approached. In the first instance, the corresponding author on the main man

<!-- TODO move to results, and keep just a short bit here -->

### Statistical analysis methods

Meta-analysis is an important method of . . .

Need formula here, and description of different methods and quarrels re fixed effect vs random effects meta-analyses.

This anal

Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on.

### Visualisation of results

Given the importance of visualising the potential biases alongside the results of any given study, a new visualisation tool was designed to allow for "paired" forest plots (as recommended by the ROB2 publication)

A summary of this tool is contained in Appendix \@ref (), .

### Assessment of added value of including preprint

Preprints are a valuable vidence source (see Introduction) but their inclusion in a systematic reivew

Additionally, I followed preprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints give you a look into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a different.

I also sought to explore the additional evidental value of including preprints in the meta-analysis, assessed using the fixed effect weight from a standard meta-analysis.

@@

&nbsp;

<!----------------------------------------------------------------------------->
(ref:gwet-caption) Suggested ranges to aid in interpretation of Gwet's AC1 inter-rater reliability metric

(ref:gwet-scaption) Ranges for Gwet's AC1

```{r gwet-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;

@@

<!--- TODO Need example table here, showing relevant cells --->

@@

<!-- TODO This needs to use the PRISMA2020 package -->

@@

### Publication bias {#sys-rev-pub-bias}

@@

One particularly interesting meta-bias potentially applicable in this review is the definition of code lists across

@@

As part of the reflective element of this thesis,

@@

Average time to complete a s

However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. <!-- TODO CITATION NEEDED - Cite Triccios new paper here -->

@@

## References

### 2021-06-01 04-Chp-CPRD-Analysis.Rmd
End of day: -3464

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
source("R/helper.R")
options(scipen = 99)
knitr::read_chunk("R/Chp3-CPRD-Analysis.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

@@

>>>>

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
source("R/helper.R")
options(scipen = 99)
knitr::read_chunk("R/04-Code-CPRD-Analysis.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

@@

<!-- TODO Will need to expand on choice of time axis here -->

### 2021-06-01 97-Discussion.Rmd
End of day: 0
End of day: -2681
End of day: -3464

# Discussion {#discussion-heading}

## Triangulation

@@

* That systematic review should no be

@@

## Public involvement and engagement

@@

## Conclusions

>>>>

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
Hold
```
(ref:intro-quote) --- Hold

# Discussion {#discussion-heading}
\minitoc <!-- this will include a mini table of contents-->

## Triangulation across exisiting evidence and evidence produced in this thesis

Using the review of the literature as a guide to identify useful further studies that could be performed, I then performed .

@@

@@

## Public involvement and engagement {#disc-PPI}

@@

## Overall conclusions
